
##CABIN Data Exploration

Preliminary wrangling, tidying and exploration for benthic data within all regions sampled in Canada within the Canadian Aquatic Biomonitoring Network (CABIN). 

CABIN is an aquatic biomonitoring program for freshwater ecosystems that began in 1987. Technicians sample benthic invertebrates at two different types of sites: Reference and Test sites.

Reference sites represent sites without industrial, agriculture, or development activity. Test sites may or may not have similar activity, and data from the reference sites is used to assess changes to macroinvertebrate communities, water chemistry, and habitat. 

Here, we graphically explore the differences between test and reference sites to see if a) we can detect a difference between these sites and b) what those differences are.


```{r}

library(png)
library(dplyr)
library(tidyverse)
library(reticulate)
library(zoo)
library(lubridate)
library(ggplot2)
library(sf)
library(mapview)
library(gridExtra)
library(data.table)
library(scales) 
library(sqldf)

install.packages("hexbin")

#library(lme4)
#library(AICcmodavg)
#library(MASS)

```

##A) Load in the data:
Benthic CABIN data in one dataframe, with a column of the Region

```{r}

library(data.table)
files <- list.files(path = "/Users/LevyJ/Desktop/CABIN", pattern = "^cabin_benthic.*?\\.csv", full.names = TRUE) 
df_benthic <- map_df(files, ~read_csv(., col_types = cols(.default = "c")), .id = "Region", encoding = 'Latin-1') 

```

Load in Study (meta) CABIN data in one dataframe, with a column of the Region.
This has the lat/long coordinates

```{r}

library(data.table)
files <- list.files(path = "/Users/LevyJ/Desktop/CABIN", pattern = "^cabin_study.*?\\.csv", full.names = TRUE) 
df_study <- map_df(files, ~read_csv(., col_types = cols(.default = "c")), .id = "Region", encoding = 'Latin-1') 

```

Load in the Habitat data, with a column for each Region. 

```{r}

library(data.table)
files <- list.files(path = "/Users/LevyJ/Desktop/CABIN", pattern = "^cabin_habitat.*?\\.csv", full.names = TRUE) 
df_habitat <- map_df(files, ~read_csv(., col_types = cols(.default = "c")), .id = "Region", encoding = 'Latin-1') 

```


##B) Benthic Data Tidying: Rename the columns to be easier to work with. 
```{r}

df_benthic <- df_benthic %>%
  rename("Site_Visit_ID" = 'SiteVisitID/IdentifiantdeVisite',
         "Site" = "Site/Site",
         "Year" = "Year/Année",
         "Sampling_Device" = "SamplingDevice/Dispositifd'échantillonnage",
         "Kick_Time" = "KickTime/Périodedelapassedufilettroubleau",
         "Mesh_size" = "MeshSize/Maillage",
         "Subsample" =	"SubSample/Sous-échantillon",
         "Julian_day" ="JulianDay/JourJulien",
         "Total_sample" ="TotalSample/Échantillontotal",
         "Status" = "Status/État",
         "Taxonomist" = "Taxonomist/Taxonomiste",
         "organization" = "Organization/Organisation",
         "address" = "Address/Adresser",
         "city" = "City/Ville",
         "province" = "Province/Province",
         "phylum" = "Phylum/Phylum",
         "class" = "Class/Classe",
         "Order" = "Order/Ordre",
         "Family" = "Family/Famille",
         "Genus" = "Genus/Genre",
         "Species" = "Species/Espèce",
         "Replicate" = "Replicate/Réplicat",
         "Count" = "Count/Décompte",
         "ITIS" ="ITIS_TSN",
         "Valid" = "Valid/Valide")

```

Benthic data tidying: Mutate a new column "unique ID" with the site visit ID, site, and year separated by a "-". This is so we have a unique id for each site visit and year.

```{r}

df_benthic <- df_benthic %>%
  tidyr::unite("Unique_Id", c("Site_Visit_ID", "Site", "Year" ), sep = "_", remove = TRUE ) 

```

Benthic data tidying: Select only kick net samples, sample # = 1, and calculate the total abundance for each unique site. Individual taxa are removed for now.

Note: should we exclude all mesh sizes for kick nets except for 400 microns? This was not done. 

```{r}

#change count column to numeric data
df_benthic$Count = as.numeric(as.character(df_benthic$Count) )

df_benthic <- df_benthic %>%
 filter( Sampling_Device == 'Kick Net') %>%
   filter(Sample_Number == '1') %>%
  group_by(Unique_Id) %>%
  mutate("Abundance" = sum(Count) ) %>%
  #removing the individual taxa for now, just using abundance
  select(Region, Unique_Id, Julian_day, Sampling_Device, Kick_Time, Mesh_size, Sample_Number, Subsample, Total_sample, Status, Abundance) %>%
  distinct()

```

Benthic data tidying/wrangling- add the region names

Load in the region names and add to the benthic data using the region names file (I made this file in excel)

```{r}

Region_names <- read.csv("Region_names.csv", colClasses =c("character", "character", "character")) 

df_benthic <- full_join(df_benthic, Region_names, by = 'Region') 

#remove file name column
df_benthic <-df_benthic %>%
  select(-c('File_Name', 'Region'))

rm(Region_names)


```

##C)Study data tidying 

(Study data columns were renamed in excel)
Mutate a new column "unique ID" with the site visit ID, site, and year separated by a "-"

```{r}

df_study <- df_study %>%
  tidyr::unite("Unique_Id", c("SiteVisitID", "Site", "Year"), sep =  "_", remove = TRUE) 

```

##D) Habitat data tidying 

Rename to make the habitat data easier to work with. Unit, year, sample_number were renamed in excel
```{r}

df_habitat <- df_habitat %>%
  rename("Site_Visit_Id" = 'SiteVisitID/IdentifiantdeVisite',
         "Site" = "Site/Site",
         "Julian_day" = "JulianDay/JourJulian",
         "Status" ="status",
         "Type" = "Type/Type",
         "Value" = "Value/Valeur",
         "Computed" = "Computed/Calculé",
         "Notes" = "Note/Remarque" ) %>%
  dplyr::select(Region, Site_Visit_Id, Site, Protocol, Julian_day, Year, Sample_Number, Status, QAQC, Type, Variable, VariableDescription, Unit, Value, MDL, Computed, Notes )

```

Habitat data tidying-
Mutate a new column "unique ID" with the site visit ID, site, and year separated by a "-"

```{r}

df_habitat <-df_habitat %>%
tidyr::unite("Unique_Id", c("Site_Visit_Id", "Site", "Year" ), sep = "_", remove = TRUE )

```

Pivot habitat data so environmental/habitat variables are in columns, values in rows to enable joining to study and benthic datasets.

Note: MDL, notes, and computed are not included, because they represent multiple observations per row.

Note: Type == River has a protocol of "Wadeable Streams" or "Small Lakes". If we separate just by protocol we could lose some river sites. 

Note: There are some NA's for protocol, double check to see if we can find out what protocol was used. They were all for older sites (see "unknown protocol" excel file)
```{r}

df_habitat <- df_habitat %>%
  #keep only first sample from triplicates
  filter(Sample_Number == "1") %>%
  #get rid of protocols other than wadeable streams
  filter(Protocol == "CABIN - Wadeable Streams") %>% 
  #ignore computed, mdl, and notes for now
  select(-c("VariableDescription", "Notes", "Computed", "MDL")) %>%
  tidyr::unite("Habitat Variable", c("Type", "Variable", "Unit"), sep = "_") %>%
  pivot_wider(names_from = "Habitat Variable", values_from = "Value") 

```


Sanity check- make sure the lengths of each new id column are the same as the length of each data frame. 
```{r}

length(unique(df_benthic$Unique_Id)) #8878
length(unique(df_study$Unique_Id)) #12464
length(unique(df_habitat$Unique_Id)) #7744
 
```

##E) Join all the data frames together

Change df to Data.tables for quicker processing speed using the data.table vignette
```{r}

setDT(df_benthic)
setDT(df_study)
setDT(df_habitat)

```


Join the three data tables together, using the habitat data as a base, because we only want to keep benthic data with the "CABIN - wadeable streams" protocol.

Note: Check on what status = 1,2,3 means for the habitat dataset. Double check that it's not necessary for delineating ref/test sites, because it was deleted from the habitat df.

```{r}

#get rid of extraneous or double columns 
df_benthic <- df_benthic %>%
  select(-c("Julian_day", "Region", "Sample_Number"))

df_habitat <- df_habitat %>%
  select(-c("Status", "Sample_Number", "Region", "Julian_day"))

#merge habitat and benthic data, keeping only the sites in the habitat data set
df_both <- merge(df_habitat, df_benthic, by= "Unique_Id", all.x = TRUE)

#merge benthic data, keeping only the sites in the hab/benth dataset.
df_all <- merge(df_both, df_study, by = "Unique_Id", all.x =TRUE)

#check:
length(unique(df_all$Unique_Id)) # should be same length as df, n=7744

rm(df_both)

```

##F)Get ready to graph

Sanity checks - count number of test, potential test, and reference sites there are. These should add to 7744

Note: There are missing values for "Status" for some sites, need to decide if we can find these or if we delete these. 
```{r}

length(unique(df_all$Unique_Id)) #7744


num_ref_sites <- sqldf( "select Status, Unique_Id
                     from df_all Where Status Like '%Refere%' ") #3605


num_test_sites <- sqldf("select Status, Unique_Id
                         from df_all where Status LIKE 'Test' ") #3776

#3605 + 3776 = 7381

#colSums(is.na(df_all)) #there are 363 Nas for "Status", likely this is where the missing NAs are from.

rm(num_ref_sites, num_test_sites)

```


Continue graphing prep! 

First graph: 

Percent sorted by region. Select only the reference or potential reference sites
```{r}

df_ref <- df_all %>%
  #changing na's this way doesn't work- likely they are listed implicitly and need to be changed to implict values (go back and do this when load in data)
  rename("Water_Chemistry_pH" = "Water Chemistry_General-pH_pH") %>%
 replace_na(list(Status = "Unknown", Subsample = "Unknown")) %>% 
  filter(Status == "Reference" | Status == "Potential Reference") %>%
  #filter(str_detect(Unique_Id_Sample, "_1$")) %>%
  mutate_at(c('Subsample'), as.numeric) 


df_test <- df_all %>%
  rename("Water_Chemistry_pH" = "Water Chemistry_General-pH_pH") %>%
  #changing na's this way doesn't work- likely they are listed implicitly and need to be changed to implict values (go back and do this when load in data)
  replace_na(list(Status = "Unknown", Subsample = "Unknown")) %>% 
  filter(Status == "Test" ) %>%
  #filter(str_detect(Unique_Id_Sample, "_1$")) %>%
  distinct() %>%
  mutate_at(c('Subsample'), as.numeric)


```


##Graph of percent sorted, by region.
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9")

ggplot(df_ref, aes(x = Region_Name, y = Subsample, fill = Region_Name )) +
geom_boxplot() +
  theme_bw() +
    theme(plot.title =  element_text(size = 10, hjust = .5, face = "bold")) +
       #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
   stat_boxplot(geom = "errorbar", width = 0.25) +
  ggtitle( "Percent Sorted by Region \n(Potential Reference or Reference Sites) ") +
  theme(legend.position = 'none') +
    #theme(legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) +
scale_x_discrete(labels = wrap_format(10)) +
  ylab("Percent Sorted") +
    scale_fill_manual(values=cbPalette) 
  
```


What is our n? How many data points are there for each region for ref/pot ref sites? 

Note: double check why the Arctic Region is left out- likely it wasn't under the wadeable stream protocol

```{r}

 dplyr::count(df_ref, Region_Name, sort = TRUE) %>%
  mutate(sum(n))

#Arctic site isn't included here?

```

##Graph of percent sorted, by region, of only test sites.

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9")

df_test %>% 
  filter(Subsample <= 100) %>%
  ggplot( aes(x = Region_Name, y = Subsample, fill = Region_Name )) +
geom_boxplot() +
  theme_bw() +
    theme(plot.title =  element_text(size = 10, hjust = .5, face = "bold")) +
       #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
   stat_boxplot(geom = "errorbar", width = 0.25) +
  ggtitle( "Percent Sorted by Region \n(Test Sites) ") +
  theme(legend.position = 'none') +
    #theme(legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) +
scale_x_discrete(labels = wrap_format(10)) +
  ylab("Percent Sorted") +
    scale_fill_manual(values=cbPalette)

#looks like there are a few outliers- graph without these
```


What is our n? How many sites are there for the test data?

Note: double check why the Arctic Region is left out- likely it wasn't under the wadeable stream protocol
```{r}

 dplyr::count(df_test, Region_Name, sort = TRUE) %>%
  mutate(sum(n))
#No data for arctic region

```

## Graph of % sorted and abundance for Reference sites - coloured by major drainage basin

```{r}

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9")


df_ref %>%
filter(Subsample <= 100) %>%
ggplot(aes(x = Subsample, y = Abundance, colour = Region_Name )) +
  geom_point(size=2) +
    theme_bw() +
    theme(plot.title =  element_text(size = 10, hjust = .5, face = "bold")) +
  ggtitle( "Percent Sorted vs Abundance \n (Ref or Potential Ref Sites) ") +
 ylab("Total Abundance (count) ") +
 xlab("Percent Sorted") +
scale_color_manual(values= cbPalette) +
theme(legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) +
    theme(legend.position=c(0.8, 0.7), legend.title=element_text(size=6), legend.text=element_text(size=6)) +
      theme(legend.title = element_text(face = "bold"))

```


## Graph of % sorted and abundance for Test sites - coloured by major drainage basin

```{r}

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9")

df_test %>%
filter(Subsample <= 100) %>%
ggplot(aes(x = Subsample, y = Abundance, colour = Region_Name )) +
  geom_point(size=2) +
    theme_bw() +
 stat_binhex() +
    theme(plot.title =  element_text(size = 10, hjust = .5, face = "bold")) +
  ggtitle( "Percent Sorted vs Abundance \n (Test Sites) ") +
 ylab("Total Abundance (count) ") +
 xlab("Percent Sorted") +
scale_color_manual(values= cbPalette) +
theme(legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) +
    theme(legend.position=c(0.8, 0.7), legend.title=element_text(size=6), legend.text=element_text(size=6)) +
      theme(legend.title = element_text(face = "bold"))

```

## Graph of % sorted and pH for Reference sites - coloured by major drainage basin

```{r}

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9")

df_ref %>%
filter(Subsample <= 100) %>%
ggplot(aes(x = Water_Chemistry_pH, y = Abundance, colour = Region_Name )) +
  geom_point(size=2) +
    theme(plot.title =  element_text(size = 10, hjust = .5, face = "bold")) +
  ggtitle( "Percent Sorted vs Abundance \n (Test Sites) ") +
scale_color_manual(values= cbPalette) +
theme(legend.background = element_rect(colour = 'black', fill = 'white', linetype='solid')) +
    theme(legend.position=c(0.8, 0.7), legend.title=element_text(size=6), legend.text=element_text(size=6)) +
      theme(legend.title = element_text(face = "bold")) 

```

## Graph of % sorted and pH for Test sites - coloured by major drainage basin

```{r}




```


## Graph of Abundance and pH for Reference sites - coloured by major drainage basin



```{r}






```

## Graph of Abundance and pH for Test sites - coloured by major drainage basin


```{r}
```


```{r}
```

